The Jester joke recommender system

### 2023-04-24 inst/ijmm_rebuttal.tex

\textcolor{blue}{Response to comment here}\\ \\

Replace Pie Charts with Pareto Charts

The pie charts are difficult to distinguish between components. For
example, in Figure 1 for 2017, the reviewers could not see a
difference between Bottas and Vettel.  The Pareto Chart style would
improve that aspect.

\textcolor{blue}{Done.  Pie charts replaced with Pareto charts}\\ \\

@@

\textcolor{blue}{Done, wta used consistently now}\\ \\

Section 2.2 Numerical Results

Explain how the WTA system maximizes the probability of the complete
order statistic.

\textcolor{blue}{Brief sentence added summarizing the comparison
  method}\\ \\

@@

Comment for Practitioners

Please include a summary of how the points system could benefit the
managers of Formula 1 and other series in the conclusion.

\textcolor{blue}{Summary added to the conclusions section.}

Overall, your analysis of Formula 1 points systems and the comparison
of points systems to an objective rank ordering has the potential to
be a valuable resource for practitioners in the motorsports industry,
helping to inform strategy, evaluate fairness, and guide
decision-making.

### 2023-05-01 inst/ijmm_rebuttal.tex

\documentclass[12pt]{article}
\usepackage{xcolor}
\begin{document}

\section*{An objective assessment of point scoring systems in Formula 1 motor racing: rebuttal}

\textcolor{blue}{
Below, I reproduce the reviewers comments; my writing, including
replies to the reviewer issues are in blue.  I have indicated changes
to the manuscript where appropriate.\\ \\
Short story: I have accommodated all the comments with rewording and
clarification.  The resulting document is, I believe, stronger and
more scholarly than before and I recommend it to you.
}

@@

Many of our readers are unfamiliar with this work.  Thus, a short
passage will help in understanding the significance of the inclusion
of Zipf in the manuscript.

\textcolor{blue}{I have realised that referring to a points system
  $\left(1,\frac{1}{2},\frac{1}{3},\frac{1}{4},\ldots\right)$ as
  ``Zipf's law'' is not really appropriate: I am not using it as a
  probability mass function but rather as a simple monotonically
  decreasing sequence.  I have removed references to ``Zipf's law'' in
  favour of the more descriptive ``Zipfian''.  I have added a sentence
  to this effect in the manuscript}\\ \\

The charts need to be larger for easier reading.  Please place figures
in full-page format as appendices.  Share the actual charts rather
than pictures of the charts.  Doing so will allow us to retain image
quality as figures are enlarged.

\textcolor{blue}{Charts now enlarged, also original PDFs supplied as
  requested}\\ \\

@@

\textcolor{blue}{Brief sentence added summarizing the comparison
  method}\\ \\

Comment for Practitioners

Please include a summary of how the points system could benefit the
managers of Formula 1 and other series in the conclusion.

\textcolor{blue}{Summary added to the conclusions section.}\\ \\

@@

Overall, your analysis of Formula 1 points systems and the comparison
of points systems to an objective rank ordering has the potential to
be a valuable resource for practitioners in the motorsports industry,
helping to inform strategy, evaluate fairness, and guide
decision-making.

\textcolor{blue}{Sentence added at the end of the document to this
  effect, slightly reworded from the reviewer's suggestion to fit
  better in context.}

### 2023-05-01 inst/jester.Rmd
use sticker in Rmd
consistentify jester to match the formula 1 data

@@

```{r,label=savejesterdataset}
save(jester,jester_maxp,file="jester.rda")
```

>>>>

## Create a table like formula 1 results table

```{r makejestertable}
jester_table <- a
for(i in seq_len(nrow(jester_table))){
  x <- jester_table[i,]
  x[!is.na(x)] <- rank(-x[!is.na(x)],ties.method="first")
  jester_table[i,] <- x
}
jester_table <- t(jester_table)
colnames(jester_table) <-paste("resp",seq_len(ncol(jester_table)),sep="_")
jester_table[1:6,1:10]
```

Above we see that respondent 1 ranked joke 8 as the funniest and joke 7 as the 15th funniest.
Comparing with `formula1_2022.txt`, for example, we see that respondents correspond to venues and jokes correspond to drivers.  We have to be a little bit careful because `NA` means "not rated", not "did not finish" as in the Formula 1 datasets.

```{r meanjokes}
plot(rowMeans(jester_table,na.rm=TRUE))
abline(v=17)
```

@@

```{r,label=savejesterdataset}
save(jester,jester_table,jester_maxp,file="jester.rda")
```
